Fitbit & ET Glasses - Methods

### 2023-02-22 02_paper/02_study/02_fitbit paper/FitBit_Plots_MK.Rmd
fitbit anova + lm mit mean_hr_std

# data wrangling - preparing data for anova
df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("ID",
         "time_span",
         "heart_rate",
         "teaching_experience",
         "disruption_factor",
         "confidence_factor") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Interviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Interviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr = mean(heart_rate, na.rm = TRUE),
            mean_confi = mean(confidence_factor, na.rm = TRUE),
            mean_disrup = mean(disruption_factor, na.rm = TRUE),
            mean_te = mean(teaching_experience, na.rm = TRUE)
         )

@@

# descriptive analysis
describeBy(df_anova$mean_hr,
           df_anova$time_span)

@@

# Visualization
bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr", add = "point")
bxp

# check for outliers
outliers <-
  df_anova %>%
  group_by(time_span) %>%
  identify_outliers(mean_hr)

@@

# QQ plot draws the correlation between a given data and the normal distribution. 
plot <- 
  ggqqplot(df_anova, "mean_hr", facet.by = "time_span")

df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr))

@@

# anova
df_anova_phase <- 
  aov(df_anova_subset$mean_hr~df_anova_subset$time_span)
summary(df_anova_phase)

# pairwise comparisons
pwc <- 
  pairwise.t.test(df_anova_subset$mean_hr, 
                  df_anova_subset$time_span, 
                  p.adjust="holm")
pwc

@@

effect_size_anova <-
  round(sqrt(0.3413791   /(1-0.3413791   )), 2)

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
effect_size_pwc <-
  df_anova_subset %>%
  cohens_d(mean_hr~time_span) %>% 
  as.data.frame()

@@

df_lm_subset <- df_anova %>% 
  filter(time_span == "Lehrphase") %>% 
  dplyr::select(mean_hr, 
               mean_disrup, 
               mean_confi,
               mean_te)

# modell rechnen
modell <-   lm(mean_hr ~ mean_confi + mean_disrup + mean_te, 
               data = df_lm_subset,
               family = binomial)
summary(modell)

@@

# standardisierte Koeffizienten
zmodell <- lm(scale(mean_hr) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
              data = df_lm_subset)
summary(zmodell)

>>>>

# data wrangling - preparing data for anova
df_anova <-
  main %>% 
  filter(time_span != "overall") %>%   
  dplyr::select("ID",
         "time_span",
         "heart_rate_std",
         "teaching_experience",
         "disruption_factor",
         "confidence_factor") %>% 
  mutate(time_span = fct_recode(time_span,
                                "Pre-Lehrphase" = "pre",
                                "Lehrphase" = "main",
                                "Post-Lehrphase" = "subsequent",
                                "Interviewphase" = "interview",
                                "Endphase" = "after"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-Lehrphase",
                                       "Lehrphase",
                                       "Post-Lehrphase",
                                       "Interviewphase",
                                       "Endphase"
                                       )
                            )
         ) %>%
  distinct() %>% 
  group_by(ID, time_span) %>%
  summarise(mean_hr_std = mean(heart_rate_std, na.rm = TRUE),
            mean_confi = mean(confidence_factor, na.rm = TRUE),
            mean_disrup = mean(disruption_factor, na.rm = TRUE),
            mean_te = mean(teaching_experience, na.rm = TRUE)
         )

@@

# descriptive analysis
describeBy(df_anova$mean_hr_std,
           df_anova$time_span)

@@

# Visualization
bxp <- ggboxplot(df_anova, x = "time_span", y = "mean_hr_std", add = "point")
bxp

# check for outliers
outliers <-
  df_anova %>%
  group_by(time_span) %>%
  identify_outliers(mean_hr_std)

@@

# QQ plot draws the correlation between a given data and the normal distribution. 
plot <- 
  ggqqplot(df_anova, "mean_hr_std", facet.by = "time_span")

df_anova_subset <- subset(df_anova, select = c(time_span, mean_hr_std))

@@

# anova
df_anova_phase <- 
  aov(df_anova_subset$mean_hr_std ~ df_anova_subset$time_span)
summary(df_anova_phase)

# pairwise comparisons
pwc <- 
  pairwise.t.test(df_anova_subset$mean_hr_std, 
                  df_anova_subset$time_span, 
                  p.adjust="holm")
pwc

@@

effect_size_anova <-
  round(sqrt(0.6533274/(1-0.6533274)), 2)

# effect size of pairwise comparisons
library(dplyr)
library(rstatix)
effect_size_pwc <-
  df_anova_subset %>%
  cohens_d(mean_hr_std ~ time_span) %>% 
  as.data.frame()

@@

df_lm_subset <- df_anova %>% 
  filter(time_span == "Lehrphase") %>% 
  dplyr::select(mean_hr_std, 
               mean_disrup, 
               mean_confi,
               mean_te)

# modell rechnen
modell <-   lm(mean_hr_std ~ mean_confi + mean_disrup + mean_te, 
               data = df_lm_subset,
               family = binomial)
summary(modell)

@@

# standardisierte Koeffizienten
zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
              data = df_lm_subset)
summary(zmodell)
